---
title: "two-way MANOVA"
author: "Dr. Amita Baranwal"
date: "`r Sys.Date()`"
output: word_document
---

Install the readxl package to import using excel file.
install.packages("readxl")
install.packages("car") to get MANOVA function
install.packages("ggplot2") to get nicer plots

R program to illustrate MANOVA test

Import required library

```{r setup, include=TRUE}
library(pandoc)
library(conflicted)
library(tidyverse)
library(carData)
library(tibble)
library(ggpubr)
library(car)
library(broom)
library(dplyr)
library(readxl)
library(ggplot2)
library(rstatix)
library(mvtnorm)
library(tidyr)


# importing excel file from local folder
data=read_excel("D:/LPU/Chapter/rice.xlsx")
glimpse(data)
```


```{r }
# Make variables factors 
block=factor(data$block)
variety=factor(data$variety)

glimpse(data)
```

here, in this example, there are two dependent or response variable (height, tillers) and two independent variables or factors (block, variety).

Null hypothesis
1. Joint mean of the response variables (height, tillers) are not significantly different among the categories of the grouping variables.

2. Joint mean of the response variables (height, tillers) are not significantly different for combinations of the block*variety interaction.

To create a model

```{r pressure, echo=FALSE}
mod <- lm(cbind(height, tillers) ~ block+variety+block*variety-1, data)
```

Note: to remove the intercept effect, we used -1 in the lm() function.

```{r }
summary(mod)
```

It can be observed from the summary Tables that there is no significant interaction effect between two independent variables. 

To run the MANOVA

```{r }
Manova(mod,multivariate=T,type=c("II"),test=("Wilks"))
```

```{r }
Manova(mod,multivariate=T,type=c("III"),test=("Wilks")) 
```
It can be observed from the MANOVA table that the variety is highly significant. It means at least two varieties differ significantly in mean for height    and/or number of tillers. 